\cvsection{Experience}
\begin{cventries}
    \cventry
        {Security Assurance Engineer}
        {Oracle México}
        {Guadalajara, México}
        {Nov. 2020 - PRESENT}
        {
            \begin{cvitems}
                \item {Maintenance of security-related packages for the Oracle Linux OS.}
                \item {Involved in the backporting and testing activities to certify software packages with the Federal Information Processing Standards 140-2 (FIPS).}
                \item {Technical leader responsible for the development and maintenance of the scap-security-guide package for Oracle Linux.}
                \item {Tools used for daily activities: Linux, Bash, C, Python, OVAL, jinja, git, Gitlab, Jenkins.}
            \end{cvitems}
        }
    \cventry
        {HMI Developer Jr}
        {Bosch México}
        {Guadalajara, México}
        {May. 2019 - Nov. 2020}
        {
            \begin{cvitems}
                \item {Development of HMI interfaces for instrument panel clusters using CGI tools and C++ frameworks.}
            \end{cvitems}
        }
    \cventry
        {Full-stack web developer \& Server administrator}
        {Qualified Storm Leads}
        {Guadalajara, México}
        {Jan. 2017 - Mar. 2019}
        {
            \begin{cvitems}
                \item {Developed web-based solutions and platforms for internal use of the company, as well as for managing clients and contact with them through email, SMS, and push-notifications.}
                \item {Build REST APIs to provide support for mobile applications.}
                \item {Used technologies and tools including PHP - Laravel, Javascript, Git and Gitflow, shell scripting.}
                \item {Managed company's both shared hosting servers and virtual private servers. Worked with distributed-database systems.}
            \end{cvitems}
        }
    \cventry
        {Back-end web developer}
        {Corb consultoría informática}
        {Guadalajara, México}
        {Feb. 2016 - Sep. 2016}
        {
            \begin{cvitems}
                \item {Development and maintenance of web platforms for different clients using various frameworks and technologies including Laravel, Angular2, JQuery, OAuth2.0, Wordpress, among others.}
            \end{cvitems}
        }
\end{cventries}
